\documentclass{cv}

\begin{document}

\cvheader{
\name{Mojtaba Barzegari}
\address{Leuven, Belgium} \hfill
\phone{(+32) 16 193831} \smallskip

\mail{mojtaba.barzegari@kuleuven.be} \hfill
\social{mbarzegary} \smallskip

\mailalt{mbarzegary@msn.com} \hfill
\socialTwitter{MojBarz} \smallskip

\webpage
{
	\href
	{https://mbarzegary.github.io/} 
	{mbarzegary.github.io} 
} \hfill
\socialYoutube{TuxRiders} \smallskip

}
{{pic}}

%\large

\noindent
{\footnotesize  \underline{Last Update: \today{}}}


%% ========================================

%% \section{Summary}

%% ========================================

\section{Education}

\longdatedsubsection
{Ph.D. Researcher}
{2018 -- Now} 
{Biomechanics Section, KU Leuven} 
{Leuven, Belgium} 

\begin{itemize}

\item 
\textbf{Field:} Computational Tissue Engineering

\item
\textbf{Project Title:} Mathematical and Computational Modeling of Biodegradation Behavior of Personalized Printed Implants

\item
\textbf{Supervisor:} Prof. Liesbet Geris

\end{itemize}

\longdatedsubsection
{Master of Science in Biomedical Engineering}
{2011 -- 2014} 
{Department of Life Science Engineering, University of Tehran} 
{Tehran, Iran} 

\begin{itemize}

\item 
\textbf{Major:} Biomaterials

\item
\textbf{Thesis:} Computational and Experimental Analysis of Dynamics of Urine Flow in the Lower Urinary System in the Physiological and Pathological Conditions using FSI Method

\item
\textbf{Supervisor:} Prof. Bahman Vahidi

%\item
%\textbf{GPA:} ... out of ...

\end{itemize}

\longdatedsubsection
{Bachelor of Science in Materials Science and Engineering}
{2006 -- 2011} 
{Department of Materials Engineering, Amirkabir University} 
{Tehran, Iran} 

\begin{itemize}

\item 
\textbf{Major:} Industrial Metallurgy

\item
\textbf{Thesis:} Prediction of Microshrinkage Porosities using the Permeability Parameter Modeled with Artificial Neural Networks in Al-6\%Si Alloy by Finite Volume Method

\item
\textbf{Supervisor:} Prof. S.M.H. Mirbagheri

%\item
%\textbf{GPA:} ... out of ...

\end{itemize}

%% ========================================

\section{Research Interests}

\begin{itemize}
\item
Scientific Computing
\item
Computational Engineering
\item
GPU programming and High-Performance Computing
\item
Machine Learning and Computational Intelligence
\item
Computational Biomechanics
\item
Computational Materials Science
\end{itemize}

%% ========================================

\section{Research Projects}

\subsection{Computational Tissue Engineering}

\begin{itemize}
\item
Development of open-source software BioDeg for massively-parallel simulation of biodegradation and corrosion of metallic biomaterials, {KU Leuven} \hfill 2020--2021
\item
Mathematical modeling and numerical simulation of biodegradation behavior of metallic implants and medical devices, {KU Leuven} \hfill 2018--2021
\item
Mathematical modeling and numerical simulation of bone tissue growth process, \\{KU Leuven} \hfill 2019--2021
\item 
Contribution to the development of open-source software ASLI for creating TPMS-based functionally graded scaffolds and implants, KU Leuven \hfill 2020-2021
\item
Numerical modeling of oxygen consumption and cell viability for pancreatic islets, \\{KU Leuven \& Maastricht University} \hfill 2019--2021
\item
Development of coupled models of topology optimization and metals corrosion for optimizing the shape of biodegradable medical devices, {KU Leuven \& Kyoto University} \hfill 2021
\end{itemize}

\subsection{Computational Fluid Dynamics}

\begin{itemize}
\item
Numerical modeling of foam formation process using Lattice Boltzmann method and multiphase fluid simulation, {Amirkabir University of Technology} \hfill 2013--2017
\item
Development of coupling simulation software packages to link multiphysics CFD models and AI, {Amirkabir University of Technology} \hfill 2010--2011
\item
Development of in-house CFD codes for simulating fluid flow and heat transfer in metal casting process, {Amirkabir University of Technology} \hfill 2008--2011
\end{itemize}

\subsection{Computational Biomechanics}

\begin{itemize}
\item 
Contribution to the development of open-source software TFMLab for traction force microscopy calculations of cellular movements, KU Leuven \hfill 2020
\item
Implementation of Fluid-Structure Interactions models to simulate fluid dynamics of human body fluids, {University of Tehran} \hfill 2012--2014
\end{itemize}

\subsection{Computational Materials Science}

\begin{itemize}
\item
Development of dendrite and microstructure growth models to simulate the solidification process of metals, {Amirkabir University of Technology} \hfill 2009--2011
\item
Development of heat transfer simulation codes in order to model heat treatment in metals, \\{Amirkabir University of Technology} \hfill 2008
\end{itemize}

\subsection{Machine Learning and Computational Intelligence}

\begin{itemize}
\item
Development of physics-informed neural network models to solve governing equations of tissue engineering processes (cell growth and oxygen consumption), {KU Leuven} \hfill 2020-2021
\item
Development of Privacy-Preserving Deep Learning models using Federated Learning and Differential Privacy for healthcare IoT systems, {KU Leuven \& Duke University} \hfill 2019--2020
\item
Implementation of Machine Learning models for signal processing and anomaly detection of EEG and ECG signals, {KU Leuven \& Imec} \hfill 2018--2019
\item
Implementation of ANN models to investigate complex parameters of urology diseases, \\{University of Tehran} \hfill 2013--2014
\item
Implementation of ANN models to investigate relations between porous media parameters and permeability, {Amirkabir University of Technology} \hfill 2010--2011
\end{itemize}


%% ========================================

\section{Publications}

\subsection{Publications in refereed journals}
\begin{enumerate}
\item
\textbf{M. Barzegari}, L. Geris, ``\href{https://arxiv.org/abs/2008.11057}{Highly scalable numerical simulation of coupled reaction-diffusion systems with moving interfaces}'', \textit{International Journal of High Performance Computing Applications}, vol. 35, 2021
\item
\textbf{M. Barzegari}, D. Mei, S.V. Lamaka, L. Geris, ``\href{https://doi.org/10.1016/j.corsci.2021.109674}{Computational modeling of degradation process of biodegradable magnesium biomaterials}'', \textit{Corrosion Science}, vol. 190, pp. 109674, 2021
\item
J. Barrasa Fano, A. Shapeti, A. Jorge Peñas, \textbf{M. Barzegari}, J.A. Sanz-Herrera, H. Van Oosterwyck, ``\href{https://doi.org/10.1016/j.softx.2021.100723}{TFMLAB: a MATLAB toolbox for 4D Traction Force Microscopy}'', \textit{SoftwareX}, vol. 15, pp. 100723, 2021 
\item
\textbf{M. Barzegari}, L. Geris, ``\href{https://doi.org/10.21105/jose.00089}{An open source crash course on parameter estimation of computational models using a Bayesian optimization approach}'', \textit{Journal of Open Source Education}, vol. 4, no. 40, 2021
\item
F. Firouzi, B. Farahani, \textbf{M. Barzegari}, M. Daneshmand, ``\href{https://doi.org/10.1109/JIOT.2020.3027971}{AI-Driven Data Monetization: The other Face of Data in IoT-based Smart and Connected Health}'', \textit{IEEE Internet of Things Journal}, 2020
\item
\textbf{M. Barzegari}, B. Vahidi, M.R. Safarinejad, M. Ebad, ``\href{https://doi.org/10.1007/s11517-020-02148-2}{A computational analysis of the effect of supporting organs on predicted vesical pressure in stress urinary incontinence}'', \textit{Medical \& Biological Engineering \& Computing}, vol. 58. no. 5, pp. 1079-1089, 2020
\item
B. Farahani, \textbf{M. Barzegari}, F. Shams Aliee, K. A. Shaik, “\href{https://doi.org/10.1016/j.micpro.2019.102938}{Towards collaborative intelligent IoT eHealth: From device to fog, and cloud}'', \textit{Microprocessors and Microsystems}, vol. 72, p. 102938, 2020
\item
\textbf{M. Barzegari}, H. Bayani, S. M. H. Mirbagheri, and H. Shetabivash, “\href{https://doi.org/10.1016/j.jmrt.2018.03.010}{Multiphase aluminum A356 foam formation process simulation using lattice Boltzmann method}'', \textit{Journal of Materials Research and Technology}, vol. 8, no. 1, pp. 1258–1266, 2019
\item
H. Bayani, S. M. H. Mirbagheri, \textbf{M. Barzegari}, and S. Firoozi, ``\href{http://www.sciencedirect.com/science/article/pii/S2238785413001129}{Simulation of Unconstrained Solidification of A356 Aluminium Alloy on Distribution of Micro/Macro Shrinkage}'', \textit{Journal of Materials Research and Technology}, vol. 3, no. 1, pp. 55-70, 2014
\end{enumerate}

\subsection{Publications as Book Chapters}

\begin{enumerate}
\item
F. Firouzi, B. Farahani, F. Ye, \textbf{M. Barzegari}, “\href{https://link.springer.com/chapter/10.1007\%2F978-3-030-30367-9_5}{Machine Learning for IoT}'', \textit{Intelligent Internet of Things}, Springer International Publishing, pp. 243–313, 2020
\item
S. M. H. Mirbagheri, H. Bayani, \textbf{M. Barzegari}, S. Firoozi, ``\href{https://www.intechopen.com/books/computational-fluid-dynamics-technologies-and-applications/simulation-of-liquid-flow-permeability-for-dendritic-structures-during-solidification-process}{Simulation of Liquid Flow Permeability for Dendritic Structures during Solidification Process}'', \textit{Computational Fluid Dynamics Technologies and Applications}, Intec, 2011
\end{enumerate}

\subsection{Preprints and Submitted Papers}
\begin{enumerate}
\item
\textbf{M. Barzegari}, H. Bayani, S. M. H. Mirbagheri, ``\href{https://arxiv.org/abs/1708.01608}{A Criterion for Bubble Merging in Liquid Metal: Computational and Experimental Study}'', arXiv Preprint
\item
\textbf{M. Barzegari}, B. Vahidi, M. R. Safarinejad, M. Hashemipour ``\href{https://arxiv.org/abs/1803.01843}{Pathological Analysis of Stress Urinary Incontinence in Females using Artificial Neural Networks}'', arXiv Preprint
\end{enumerate}

\subsection{Publications in refereed conference proceedings}
\begin{enumerate}
\item
F. Firouzi, B. Farahani, E. Panahi, \textbf{M. Barzegari}, ``\href{https://ieeexplore.ieee.org/abstract/document/9524098}{
Task Offloading for Edge-Fog-Cloud Interplay in the Healthcare Internet of Things (IoT)}'', \textit{Proceedings of the International Conference on Omni-Layer Intelligent Systems}, 2021
\item
B. Farahani, \textbf{M. Barzegari}, F. Shams Aliee, ``\href{https://dl.acm.org/citation.cfm?id=3312644}{
Towards Collaborative Machine Learning Driven Healthcare Internet of Things}'', \textit{Proceedings of the International Conference on Omni-Layer Intelligent Systems}, Crete, Greece, 2019 
\end{enumerate}

\subsection{Conference and symposium abstracts (as main presenter)}

\begin{enumerate}
\item
(Oral presentation)
\textbf{M. Barzegari}, L. Geris, (2021), "Physics-informed neural network model for cell viability and oxygen consumption of pancreatic islets". Mechanistic Machine Learning and Digital Twins for Computational Science, Engineering \& Technology conference (MMLDT), Virtual, Sep 2021
\item
(Oral presentation)
\textbf{M. Barzegari}, L. Geris, (2021), "High-performance computing in biomedical engineering; a use-case for biomaterials degradation modeling". 17th International Symposium on Computer Methods in Biomechanics and Biomedical Engineering (CMBBE), Virtual, Sep 2021
\item
(Oral presentation)
\textbf{M. Barzegari}, D. Mei, S.V. Lamaka, L. Geris, (2021), "Mathematical modeling of degradation process of biodegradable metallic biomaterials in immersion and perfusion setups". XXVIII Congress of the International Society of Biomechanics (ISB), Virtual, July 2021
\item
(Oral presentation)
\textbf{M. Barzegari}, L. Geris, (2021), "Mathematical modeling of biodegradation of metallic biomaterials using reaction-diffusion equations and level set method". SIAM Conference on Mathematical Aspects of Materials Science, Virtual, May 2021
\item
(Oral presentation)
\textbf{M. Barzegari}, L. Geris, (2021), "Reproducible research in computational sciences: A use case for uncertainty quantification using Jupyter notebooks". KU Leuven Open Science Study Day, Virtual, Apr 2021
\item
(Oral presentation)
\textbf{M. Barzegari}, L. Geris, (2021), "Investigating the Biodegradation of Metallic Biomaterials using HPC-Based Simulation Techniques". 14th World Congress on Computational Mechanics, Virtual, Jan 2021
\item
(Oral presentation) 
\textbf{M. Barzegari}, L. Geris, (2020). "Computational modeling of in-vitro biodegradation of metallic scaffolds and bone implants". 11th World Biomaterials Congress, Virtual, Dec 2020
\item
(Poster presentation) 
\textbf{M. Barzegari}, L. Geris, (2020). "Jupyter for uncertainty quantification and parameter estimation of computational models". JupyterCon, Virtual, Oct 2020
%\item
%(Oral presentation) 
%\textbf{M. Barzegari}, L. Geris, (2020). "Mathematical modeling of biodegradation of metallic biomaterials using reaction-diffusion equations and level set method". SIAM Conference on Mathematical Aspects of Materials Science, Bilbao, Spain, May 2020
\item
(Oral presentation) 
\textbf{M. Barzegari}, L. Geris, (2019). "High-performance numerical simulation of biodegradation process with moving boundaries". FreeFEM Days, 11th Edition, Paris, France, Dec 2019
\item
(Oral presentation) 
\textbf{M. Barzegari}, L. Geris, (2019). "Computational Modeling Of Biodegradation Of Metallic Biomaterials". 18th National Day on Biomedical Engineering, Brussels, Belgium, Nov 2019
\item
(Poster presentation) 
\textbf{M. Barzegari}, L. Geris, (2019). "Developing a mathematical model of biodegradable metallic scaffolds for bone tissue engineering applications". 7th Belgian Symposium on Tissue Engineering, Hasselt, Belgium, Nov 2019
\item
(Oral presentation) 
\textbf{M. Barzegari}, F.P. Boerema, L. Geris, (2019). "Computational optimization and biodegradation of 3D-printed patient-specific acetabular implants". European Orthopaedic Research Society (EORS) 2019, Maastricht, the Netherlands, Oct 2019
\item
(Oral presentation) 
\textbf{M. Barzegari}, L. Geris, (2019). "High-performance simulation of biodegradation behavior of magnesium-based biomaterials". Fluid and solid mechanics for tissue engineering, Oxford, UK, Sep 2019
\item
(Oral presentation) 
\textbf{M. Barzegari}, L. Geris, (2019). "Numerical simulation of biodegradation and corrosion of magnesiumbased orthopedic implants". 2nd International Conference on Simulation for Additive Manufacturing, Pavia, Italy, Sep 2019
\item
(Oral presentation) 
\textbf{M. Barzegari}, L. Geris, (2019). "Mathematical modeling of biodegradation of metal implants in orthopedics". 11th Symposium on Biodegradable Metals, Alicante, Spain, Aug 2019
\end{enumerate}

\subsection{Conference and symposium abstracts (as co-author)}

\begin{enumerate}
\item
R. de Vries, \textbf{M. Barzegari}, S. Mohammed, A. Stell, C. Hermanns, M. Jetten, D. de Bont, O.P. da Silva Filho, V. Vaithilingam, A Carlier, L. Geris, A. van Apeldoorn, (2021), "Upscaling of a Next Generation Microwell-Based Beta Cell Replacement Device". 6th TERMIS World Congress on Tissue Engineering and Regenerative Medicine (TERMIS), Nov 2021
\item
F. Perez-Boerema, \textbf{M. Barzegari}, L. Geris, (2021), "Creating your own TPMS-based functionally graded scaffolds for 3D-printing". 17th International Symposium on Computer Methods in Biomechanics and Biomedical Engineering (CMBBE), Sep 2021
\item
J.B. Fano, A. Shapeti, M. Cóndor, J. De Jong, A.A. Fernández, \textbf{M. Barzegari}, J.A. Sanz-Herrera, H. van Oosterwyck, (2021), "Quantifying cellular forces in a 3D in vitro vascular model". 17th International Symposium on Computer Methods in Biomechanics and Biomedical Engineering (CMBBE), Sep 2021
\end{enumerate}


\subsection{Publications in non-English (Persian) journals and proceedings}
\begin{enumerate}
\item
\textbf{M. Barzegari}, B. Vahidi, M. R. Safarinejad, ``\href{http://mme-old.modares.ac.ir/article_16771_en.html}{Investigating Stress Urinary Incontinence in Women Using Computational Methods and Clinical Data}", \textit{Journal of Modares Mechanical Engineering}, vol. 17, no. 5, pp. 417-427, 2017 %[Persian]
\item
\textbf{M. Barzegari}, B. Vahidi, M. R. Safarinejad, ``\href{https://www.civilica.com/Paper-ISME25-ISME25_342.html}{Computational Simulation of Stress Urinary Incontinence using Fluid-Structure Interaction Analysis}", \textit{25th International Conference on Mechanical Engineering}, Tehran, Iran, 2017
\item
\textbf{M. Barzegari}, H. Bayani, S. M. H. Mirbagheri, ``\href{https://www.civilica.com/Paper-ISME25-ISME25_710.html}{Computational and Experimental Investigation of Air Bubbles Coalescence in Metal Melts}", \textit{25th International Conference on Mechanical Engineering}, Tehran, Iran, 2017
\item
S. Gholami, A. Danayi, A. Rezaee, \textbf{M. Barzegari}, ``\href{https://civilica.com/doc/656407/}{Embedded Systems and the Challenge of Complex Computing in Internet of Things}", \textit{1st International Conference on Internet of Things, Applications and Infrastructure}, Isfahan, Iran, 2017
\item
S. M. H. Mirbagheri, H. Bayani, \textbf{M. Barzegari}, ``\href{https://1drv.ms/b/s!Av7P45pSaDtYgUnsN3LHLbiNHomt}{Micro Shrinkages Simulation in Mushy Zone by Permeability Calculation}", \textit{Journal of Iranian Foundrymen's Society}, vol. 102, pp. 42-50, 2013 %[Persian]
\item
\textbf{M. Barzegari}, S. M. H. Mirbagheri, ``\href{http://jmme.um.ac.ir/index.php/metallurgical/article/view/10905}{Assessment of the Slope and Cross-Section of In-Gate on the Pressure and Flow Pattern Using Finite Volume Method}", \textit{Journal of Metallurgical and Materials Engineering}, vol. 22, no. 2, pp. 21-36, 2011 %[Persian]
\end{enumerate}


%% ========================================

\section{Teaching Experiences}

\subsection{Teaching Assistance}


\begin{itemize}
\item 
\href{https://github.com/mbarzegary/mass-transport-tissue-engineering-spring2021}{Mass transfer in tissue engineering} (MSc), KU Leuven \hfill 2020-2021
\item 
Transport phenomena in biomedical engineering (BSc), KU Leuven \hfill 2020
\item 
Musculoskeletal biomechanics (BSc), KU Leuven \hfill 2020
\end{itemize}
	
\subsection{Supervision and Mentoring}

\begin{itemize}
\item 
Mr. Kwinten Van Meerbeek, MSc thesis project: "Can machine learning replace the computer models of tissue engineering? Towards using physics-informed neural network models for computer simulations", KU Leuven \hfill 2021--2022
\item 
Mr. Tijs Vanbosseghem, MSc thesis project: "What happens to biodegradable implants inside the body? Studying the controlled release and
degradation of the metallic biomaterials using finite element simulations", KU Leuven \hfill 2021--2022
\item 
Mr. Pieter Ansoms, MSc thesis project: "Finite element analysis of mechanical behavior during the implant biodegradation process", KU Leuven \hfill 2020--2021
\item
Daily supervisory of 15 students (mechanical engineering) for the "Problem Solving and Design" course on "Improving a pre-cleaner design" project, KU Leuven \hfill 2019--2020
\end{itemize}

\subsection{Workshops}

\begin{itemize}
\item
``\href{https://www.youtube.com/watch?v=3nIExqK49n4}{Open Source in Multi-Scale Modeling}'', \textsc{1st SGABU Project Workshop, Virtual} \hfill 2021
\item
``\href{https://www.slideshare.net/tehsfd/embedded-system-70659214}{Towards Embedded Systems, Motivational Role of Free Software}'', \textsc{Tehran Software Freedom Day Festival, Sharif University of Technology} \hfill 2016
\item
``An introduction to \LaTeX{} for thesis typesetting", \textsc{University of Tehran} \hfill 2013
\end{itemize}


\subsection{Unofficial/Community Teaching}

\begin{itemize}
\item
Advanced programming for electrical engineering students \hfill 2016
\item
Metal casting simulation for mechanical engineering students \hfill 2014
\item
Scientific computing concepts for biomedical engineering students \hfill 2011
\item
Computer basics and mathematics for kids \hfill 2013-2016
\end{itemize}

%% ========================================

\section{Service and Outreach}

\subsection{External Reviewing}

\begin{itemize}
\item
Journal of Computational Science\hfill 2021
\item
Part C: Journal of Mechanical Engineering Science\hfill 2021
\item
Frontiers in Bioengineering and Biotechnology\hfill 2021
\item
IEEE Conference on Omni-Layer Intelligent Systems\hfill 2021
\item
Journal of Open Source Education\hfill 2021
\item
Multimedia Tools and Applications (for machine learning topics)\hfill 2020-2021
\end{itemize}

\subsection{Scientific Community}

\begin{itemize}
\item
Co-chair of special session ``Necessity and importance of high-performance computing to address the scalability issue of biomedical-related computational studies'' in CMBBE conference\hfill 2021
\item
Co-chair of session ``Biomaterials for musculoskeletal application'' in TERMIS conference\hfill 2021
\item
Scientific coordinator of the youngster committee of Belgium National Committee on Biomedical Engineering (NCBME) \hfill 2020-2021
\item
Member of Virtual Physiological Human Institute (VPHi) student committee \hfill 2021
\end{itemize}

\subsection{Science Outreach}

\begin{itemize}
\item
Active member of FreeFEM community (\href{https://community.freefem.org/}{community.freefem.org}) \hfill 2019-2021
\item
Blogging on technical aspects of scientific computing (\href{https://mbarzegary.github.io/blog}{mbarzegary.github.io/blog})\hfill 2020-2021
\item
Constantly share the developed models and codes on GitHub (\href{https://github.com/mbarzegary}{github.com/mbarzegary}) \hfill 2018-2021
\item
Starting TuxRiders project for sharing open-source scientific computing experiences \hfill 2021
\\ (\href{http://www.tuxriders.com/}{TuxRiders.com}) (\href{https://www.youtube.com/TuxRiders}{youtube.com/TuxRiders})
\begin{itemize}
\item 35 videos, \textasciitilde 5,000 views (in 7 months)
\item \textasciitilde 120 subscribers (in 7 months)
\end{itemize}
\end{itemize}


%% ========================================

\section{Awards}

\begin{itemize}
\item
Best short oral and poster presentation prize in the corrosion topic, Biometal symposium \hfill 2019
\item
Best hands-on project prize on "Machine learning and mechanistic tissue modeling for image-guided brain surgery", VPH Summer School \hfill 2019
\item
Awarded researcher of the Department of Materials Science and Engineering, Amirkabir University of Technology \hfill 2011
\item
2nd Place in Khwarizmi young award of scientific innovation in the field of mathematics (project title: mathematical computation and function plotting software) \hfill 2004
\end{itemize}


%% ========================================

\section{Professional Projects and Work Experiences}


Selected projects (among 20 more) in 15 years of professional software development and computer programming experiences (2003--2017):

\subsection{Internet of Things \& Embedded Systems}

\begin{itemize}

\item
Design and implementation of smart home solutions based on IoT and Cloud Computing paradigms, Freelance projects \hfill 2016--2017
\item
Design and implementation of embedded systems and embedded Linux programs using C, C++, Python and GNU toolchains, Amirkabir University of Technology \hfill 2016--2017

\end{itemize}


\subsection{Web \& Mobile Applications}

\begin{itemize}

\item
Implementation of resources and documents management software for Iran Red Crescent Society using C\# and .NET web technologies \hfill 2015--2016
\item
Implementation of online shopping system for Parhoon Koosha Co. using PHP \hfill 2016
\item
Implementation of Android-based enterprise apps using Java and Xamarin technologies, \\Freelance projects \hfill 2015--2016
\item
Development and optimization of the UI of comprehensive medical instruments software developed in C\#, Avizheh IT Co. \hfill 2014
\item
Development of commission management software for Tehran Municipality using C\# and .NET web technologies \hfill 2011

\end{itemize}


\subsection{Desktop \& Enterprise Applications}

\begin{itemize}

\item
Development of estate profiling software using C\#, Venus IT Co. \hfill 2013
\item
Development of Tehran districts profiling and reporting software for Tehran Municipality using C\# and .NET technologies \hfill 2012
\item
Development of office and workflow automation software for Iran Tube and Machine Manufacturing Corporation using C\# and .NET technologies, Avizheh IT Co. \hfill 2010--2011
\item
Development of project control and operational automation software for Iran Railway Corporation using VB and .NET technologies, Avizheh IT Co. \hfill 2008--2011.
\item
Development of workflow management software for Parhoon Koosha Co. using C\# and .NET technologies \hfill 2006

\end{itemize}


\subsection{Scientific Applications}

\begin{itemize}
\item
Implementation of SUTCast simulation software code in MATLAB (fluid flow and heat transfer modules), Razi Research Center of Applied Science \hfill 2015
\item
Implementation of ANN models for optimization of rolling parameters in Mobarakeh Steel Manufacturing Co. using MATLAB \hfill 2014
\item
Development of mathematical computation and function plotting software using C\# (Awarded as the 2nd place in Khwarizmi young award of scientific innovation) \hfill 2004
\item
Development of robot control software using VB, Iran Students' Foundation \hfill 2003

\end{itemize}


%% ========================================

\section{Technical Skills}

\begin{itemize}

\item
 \textbf{Operating Systems} \\ Microsoft Windows (Client \& Server), GNU/Linux (Desktop \& Embedded)
 \item
\textbf{Programming Languages \& Frameworks}\\  C, C++, C\#, Python, Java, Visual Basic, T-SQL, ActionScript, Qt, .NET and .NET Core, Android app development, Xamarin, Universal Windows Platform (UWP), Arduino
\item
\textbf{Scientific Computing}\\  MATLAB \& GNU Octave, Maple, FreeFEM, FEniCS, OpenFOAM
\item 
\textbf{Parallel Computing}\\ MPI, PETSc, OpenMP, OpenACC, CUDA
\item
\textbf{Machine Learning}\\ Scikit-learn, Keras, TensorFlow, TF Federated, SimNet, HyperOpt
\item
\textbf{Databases}\\ Microsoft SQL Server, MySQL (MariaDB), SQLite
\item
\textbf{Web Development} \\
HTML, CSS, JavaScript, PHP, ASP.NET, Django, React, Dash
\item
\textbf{Engineering Software Packages}\\ SolidWorks, ANSYS (Mechanical, Fluent, Explicit Dynamics \& AUTODYN), ProCAST, MSC Patran, MD ADAMS, COMSOL, FreeCAD, SALOME, GMSH, ParaView
\item
\textbf{Other}\\  \LaTeX{}, Docker, Git

\end{itemize}

%% ========================================

\section{Personal Details}

\begin{itemize}

\item
\textbf{Date of Birth:}
February 25th, 1988

%\item
%\textbf{Sex and Status:}  
%... and ...

\item
{\bf Nationality:}
Iranian

\item
\textbf{Languages Known:}
\begin{itemize}

\item
Persian: Native

\item
English: Fluent
%TOEFL iBT: 106 out of 120 
%(Exam Date: 14.Oct.2017)
%\begin{itemize}
%
%\item
%Reading: 29, 
%Listening: 23, 
%Speaking: 27,
%Writing: 27 
%\end{itemize}
\end{itemize}

\item
\textbf{Extracurricular Activities:}

\begin{itemize}
\item
Amateur guitar playing (bass player of folk band "Me, Moon, and You")
\item
Playing volleyball \& chess (member of Eindhoven student chess club  Noesis)
\item
Swimming \& biking
\item
Playing computer \& mobile games
\item
Reading science, music, and history books
\end{itemize} 


\end{itemize}

%% ========================================

%\section{References}
%
%\begin{enumerate}
%
%\item
%Prof. Liesbet Geris:
%\begin{itemize}
%
%\item[]
%\faMapMarker \,\, KU Leuven, Leuven, Belgium
%
%\item[]
%\faPhone \,\,  +32 16 372690
%
%\item[]
%\faEnvelope \,\, liesbet.geris@kuleuven.be
%\hfill
%\faInternetExplorer \,\, \href{https://www.kuleuven.be/wieiswie/en/person/35945}{kuleuven.be/wieiswie/en/person/35945} 
%\end{itemize}
%
%\item
%Prof. S. M. H. Mirbagheri:
%\begin{itemize}
%
%\item[]
%\faMapMarker \,\, Amirkabir University of Technology, Tehran, Iran
%
%\item[]
%\faPhone \,\, +98 21 64542961
%
%\item[]
%\faEnvelope \,\, smhmirbagheri@aut.ac.ir
%\hfill
%\faInternetExplorer \,\, \href{http://www.aut.ac.ir/smhmirbagheri}{aut.ac.ir/smhmirbagheri} 
%\end{itemize}
%
%\item
%Prof. Bahman Vahidi:
%\begin{itemize}
%
%\item[]
%\faMapMarker \,\, University of Tehran, Tehran, Iran
%
%\item[]
%\faPhone \,\, +98 21 86093021
%
%\item[]
%\faEnvelope \,\, bahman.vahidi@ut.ac.ir
%\hfill
%\faInternetExplorer \,\, \href{http://fnst.ut.ac.ir/en/~bahman.vahidi}{fnst.ut.ac.ir/en/bahman.vahidi}
%
%	
%\end{itemize}
%
%\end{enumerate}

%% ========================================

\end{document} ​
